Tables in the project

### 2018-08-09 paper/Chapters/Chapter3.tex
BMI table hypertension results added

\textbf{Table \ref{tab:tab1hypetension}} presents the characteristics of men and women participants in the NDNS RP 2008/09-15/16 by hypertension status. The weighted prevalences of hypertension were 30.4\% in men and 27.5\% in women. Among both sexes, there were significant differences by hypertension status for age, education level, living with a partner or not, smoking status, BMI, WC, and prevalence of diabetes (\textit{p} < 0.01). Differences were also found for carbohydrate eating patterns defined previously, and total energy intake, as well as total carbohydrate intake (\textit{p} < 0.001). No difference was found among either men or women for geographic location, and ethnicity. Strong evidence of difference was found in women for average household income (32741.5 \textsterling/year in non-hypertensive vs. 27862.0 \textsterling/year in hypertensive, \textit{p} < 0.001), and physical activity level (geometric mean: 0.81 hours/day in non-hypertensive compared with 0.53 hours/day in hypertensive, \textit{p} < 0.001) but not in men.

@@

	\caption{\label{tab:tab2HYT} ORs (95\%CI) of carbohydrate eating patterns with hypertension with or without diabetes in the UK adults.\\ (NDNS RP 2008/09-2015/16, sample size = 6155)}
	\centering
	\fontsize{9}{11}\selectfont
	\begin{tabular}[t]{lccccc}
		\hiderowcolors
		\toprule
		\multicolumn{1}{c}{ } & \multicolumn{5}{c}{\textbf{Carbohydrate eating patterns}} \\
		\cmidrule(l{2pt}r{2pt}){2-6}
		\textbf{Model} & \textbf{Low} & \textbf{Moderate} & \textbf{\textit{P} value\textsuperscript{*}} & \textbf{High} & \textbf{\textit{P} value\textsuperscript{*}}\\
		\midrule
		\showrowcolors
		\addlinespace[0.3em]
		\multicolumn{6}{l}{\textbf{Men (n = 2537)}}\\
		\addlinespace[0.3em]
		\multicolumn{6}{l}{\hspace{1em}\textbf{Hypertension}}\\
		\hspace{1em}\hspace{1em}Crude model & 1 & 0.48 (0.33, 0.70) & < 0.001 & 0.82 (0.59, 1.13) & 0.217\\
		\hspace{1em}\hspace{1em}Model 1\textsuperscript{\dag} & 1 & 0.68 (0.43, 1.07) & 0.093 & 0.80 (0.56, 1.15) & 0.227\\
		\hspace{1em}\hspace{1em}Model 2 & 1 & 0.64 (0.41, 1.01) & 0.054 & 0.75 (0.53, 1.08) & 0.124\\
		\addlinespace[0.3em]
		\multicolumn{6}{l}{\hspace{1em}\textbf{Hypertension in non-diabetics}}\\
		\hspace{1em}\hspace{1em}Crude model & 1 & 0.49 (0.33, 0.73) & < 0.001 & 0.82 (0.59, 1.14) & 0.241\\
		\hspace{1em}\hspace{1em}Model 1 & 1 & 0.69 (0.43, 1.09) & 0.11 & 0.78 (0.54, 1.14) & 0.197\\
		\hspace{1em}\hspace{1em}Model 2 & 1 & 0.65 (0.41, 1.03) & 0.066 & 0.73 (0.51, 1.06) & 0.096\\
		\addlinespace[0.3em]
		\multicolumn{6}{l}{\textbf{Women (n = 3618)}}\\
		\addlinespace[0.3em]
		\multicolumn{6}{l}{\hspace{1em}\textbf{Hypertension}}\\
		\hspace{1em}\hspace{1em}Crude model & 1 & 0.52 (0.36, 0.75) & < 0.001 & 0.96 (0.72, 1.28) & 0.773\\
		\hspace{1em}\hspace{1em}Model 1\textsuperscript{\ddag} & 1 & 0.79 (0.45, 1.39) & 0.415 & 0.89 (0.61, 1.30) & 0.552\\
		\hspace{1em}\hspace{1em}Model 2 & 1 & 0.78 (0.45, 1.36) & 0.384 & 0.88 (0.62, 1.26) & 0.483\\
		\addlinespace[0.3em]
		\multicolumn{6}{l}{\hspace{1em}\textbf{Hypertension in non-diabetics}}\\
		\hspace{1em}\hspace{1em}Crude model & 1 & 0.51 (0.35, 0.74) & < 0.001 & 0.98 (0.73, 1.31) & 0.875\\
		\hspace{1em}\hspace{1em}Model 1 & 1 & 0.79 (0.44, 1.42) & 0.435 & 0.89 (0.61, 1.29) & 0.534\\
		\hspace{1em}\hspace{1em}Model 2 & 1 & 0.79 (0.45, 1.39) & 0.415 & 0.87 (0.61, 1.25) & 0.452\\
		\bottomrule
		\multicolumn{6}{l}{{\scriptsize \textit{Note: }}}\\
		\multicolumn{6}{l}{{\scriptsize \textbf{Abbreviations}: BMI body mass index; WC, waist circumference; NDNS RP, national}}\\
		\multicolumn{6}{l}{{\scriptsize dietary and nutrition survey rolling programme.}}\\
		\multicolumn{6}{l}{{\scriptsize Diabetes was defined by A1C > 6.5\%. BMI was replaced with WC in Model 2s, other}}\\
		\multicolumn{6}{l}{{\scriptsize covariates remained the same with the corresponding Model 1s.}}\\
		\multicolumn{6}{l}{{\scriptsize \textsuperscript{*} \textit{P} values were obtained from wald tests from either linear regression models or logistic}}\\ 
		\multicolumn{6}{l}{{\scriptsize regression models.}}\\
		\multicolumn{6}{l}{{\scriptsize \textsuperscript{\dag} Adjusted for age (continuous), live with partner or not (binary), education level}}\\ 
		\multicolumn{6}{l}{{\scriptsize (higher or equal to degree level or not), BMI, smoking status (current, ex-smoker, never)}}\\
		\multicolumn{6}{l}{{\scriptsize , total energy intake (kJ);}}\\
		\multicolumn{6}{l}{{\scriptsize \textsuperscript{\ddag} Adjusted for age, live with partner or not, average household income (continuous),}}\\ 
		\multicolumn{6}{l}{{\scriptsize education level, BMI, smoking status, total energy intake (kJ), alcohol consumption (g/day);}}\\
	\end{tabular}
\end{table}

@@

>>>>

\textbf{Table \ref{tab:tab1hypetension}} presents the characteristics of men and women participants in the NDNS RP 2008/09-15/16 by hypertension status. The weighted prevalences of hypertension were 30.4\% in men and 27.5\% in women. Among both sexes, there were strong evidence of differences by hypertension status for age, education level, living with a partner or not, smoking status, BMI, WC, and prevalence of diabetes (\textit{p} < 0.01). Differences were also found for carbohydrate eating patterns defined previously, total energy intake, as well as total carbohydrate intake (\textit{p} < 0.001). No difference was found among either men or women for geographic location, and ethnicity. Strong evidence of difference was found in women for average household income (32741.5 \textsterling/year in non-hypertensive vs. 27862.0 \textsterling/year in hypertensive, \textit{p} < 0.001), and physical activity level (geometric mean: 0.81 hours/day in non-hypertensive compared with 0.53 hours/day in hypertensive, \textit{p} < 0.001) but not in men.

The sex-specific associations of carbohydrate eating patterns with hypertension with or without diabetes are shown in \textbf{Table \ref{tab:tab2HYT}}. In the crude models, moderate carbohydrate eaters had statistically significant lower odds of having hypertension than low carbohydrate eaters in both men and women irrespective to diabetes status. Among men, after adjustment for selected confounders, which includes: age, live with partner or not, education level, BMI, smoking status, and total energy intake, the odds ratio (OR) comparing moderate carbohydrate eaters was 0.68 (95\% CI: 0.43, 1.07) and remained borderline significant (\textit{p} = 0.093). 95\% CI of the OR became narrower (OR: 0.64, 95\% CI: 0.41, 1.01, \textit{p} = 0.054) when BMI was replaced with WC in model 2. When diabetic men were excluded in the models, the ORs (95\%CI) for moderate and high carbohydrate eaters compared with low carbohydrate eaters were 0.65 (0.41, 1.03) and 0.73 (0.51, 1.06), respectively. The negative associations between carbohydrate eaters patterns were still observed in women, however, without any statistical evidence in the full adjusted models. \vspace{-0.3cm}

\subsubsection{Obesity (BMI and WC)}\vspace{-0.3cm}

@@

	\caption{\label{tab:tab2HYT} ORs (95\%CI) of carbohydrate eating patterns with hypertension in the UK adults, with or without diabetes .\\ (NDNS RP 2008/09-2015/16, sample size = 6155)}
	\centering
	\fontsize{9}{11}\selectfont
	\begin{tabular}[t]{lccccc}
		\hiderowcolors
		\toprule
		\multicolumn{1}{c}{ } & \multicolumn{5}{c}{\textbf{Carbohydrate eating patterns}} \\
		\cmidrule(l{2pt}r{2pt}){2-6}
		\textbf{Model} & \textbf{Low} & \textbf{Moderate} & \textbf{\textit{P} value\textsuperscript{*}} & \textbf{High} & \textbf{\textit{P} value\textsuperscript{*}}\\
		\midrule
		\showrowcolors
		\addlinespace[0.3em]
		\multicolumn{6}{l}{\textbf{Men (n = 2537)}}\\
		\addlinespace[0.3em]
		\multicolumn{6}{l}{\hspace{1em}\textbf{Hypertension}}\\
		\hspace{1em}\hspace{1em}Crude model & 1 & 0.48 (0.33, 0.70) & < 0.001 & 0.82 (0.59, 1.13) & 0.217\\
		\hspace{1em}\hspace{1em}Model 1\textsuperscript{\dag} & 1 & 0.68 (0.43, 1.07) & 0.093 & 0.80 (0.56, 1.15) & 0.227\\
		\hspace{1em}\hspace{1em}Model 2 & 1 & 0.64 (0.41, 1.01) & 0.054 & 0.75 (0.53, 1.08) & 0.124\\
		\addlinespace[0.3em]
		\multicolumn{6}{l}{\hspace{1em}\textbf{Hypertension in non-diabetics}}\\
		\hspace{1em}\hspace{1em}Crude model & 1 & 0.49 (0.33, 0.73) & < 0.001 & 0.82 (0.59, 1.14) & 0.241\\
		\hspace{1em}\hspace{1em}Model 1\textsuperscript{\dag} & 1 & 0.69 (0.43, 1.09) & 0.110 & 0.78 (0.54, 1.14) & 0.197\\
		\hspace{1em}\hspace{1em}Model 2 & 1 & 0.65 (0.41, 1.03) & 0.066 & 0.73 (0.51, 1.06) & 0.096\\
		\addlinespace[0.3em]
		\multicolumn{6}{l}{\textbf{Women (n = 3618)}}\\
		\addlinespace[0.3em]
		\multicolumn{6}{l}{\hspace{1em}\textbf{Hypertension}}\\
		\hspace{1em}\hspace{1em}Crude model & 1 & 0.52 (0.36, 0.75) & < 0.001 & 0.96 (0.72, 1.28) & 0.773\\
		\hspace{1em}\hspace{1em}Model 1\textsuperscript{\ddag} & 1 & 0.79 (0.45, 1.39) & 0.415 & 0.89 (0.61, 1.30) & 0.552\\
		\hspace{1em}\hspace{1em}Model 2 & 1 & 0.78 (0.45, 1.36) & 0.384 & 0.88 (0.62, 1.26) & 0.483\\
		\addlinespace[0.3em]
		\multicolumn{6}{l}{\hspace{1em}\textbf{Hypertension in non-diabetics}}\\
		\hspace{1em}\hspace{1em}Crude model & 1 & 0.51 (0.35, 0.74) & < 0.001 & 0.98 (0.73, 1.31) & 0.875\\
		\hspace{1em}\hspace{1em}Model 1\textsuperscript{\ddag} & 1 & 0.79 (0.44, 1.42) & 0.435 & 0.89 (0.61, 1.29) & 0.534\\
		\hspace{1em}\hspace{1em}Model 2 & 1 & 0.79 (0.45, 1.39) & 0.415 & 0.87 (0.61, 1.25) & 0.452\\
		\bottomrule
		\multicolumn{6}{l}{{\scriptsize \textit{Note: }}}\\
		\multicolumn{6}{l}{{\scriptsize \textbf{Abbreviations}: OR, odds ratio; CI, confidence interval; BMI, body mass index; WC, waist}}\\
		\multicolumn{6}{l}{{\scriptsize  circumference; NDNS RP, national dietary and nutrition survey rolling programme.}}\\
		\multicolumn{6}{l}{{\scriptsize Diabetes was defined by A1C > 6.5\%. BMI was replaced with WC in Model 2s, other}}\\
		\multicolumn{6}{l}{{\scriptsize covariates remained the same with the corresponding Model 1s.}}\\
		\multicolumn{6}{l}{{\scriptsize \textsuperscript{*} \textit{P} values were obtained from wald tests from logistic regression models.}}\\ 
		\multicolumn{6}{l}{{\scriptsize \textsuperscript{\dag} Adjusted for age (continuous), live with partner or not (binary), education level}}\\ 
		\multicolumn{6}{l}{{\scriptsize (higher or equal to degree level or not), BMI, smoking status (current, ex-smoker, never)}}\\
		\multicolumn{6}{l}{{\scriptsize , total energy intake (kJ);}}\\
		\multicolumn{6}{l}{{\scriptsize \textsuperscript{\ddag} Adjusted for age, live with partner or not, average household income (continuous),}}\\ 
		\multicolumn{6}{l}{{\scriptsize education level, BMI, smoking status, total energy intake (kJ), alcohol consumption (g/day);}}\\
	\end{tabular}
\end{table}

@@

	\caption{\label{tab:tab2BMI}Associations of carbohydrate eating patterns with BMI in the UK adults, with or without diabetes. \\ (NDNS RP 2008/09-2015/16, sample size = 6155)}
	\centering
	\fontsize{9}{11}\selectfont
	\begin{tabular}[t]{lccccc}
		\hiderowcolors
		\toprule
		\multicolumn{1}{c}{ } & \multicolumn{5}{c}{\textbf{Carbohydrate eating patterns}} \\
		\cmidrule(l{2pt}r{2pt}){2-6}
		\textbf{Model} & \textbf{Low} & \textbf{Moderate} & \textbf{\textit{P} value\textsuperscript{*}} & \textbf{High} & \textbf{\textit{P} value\textsuperscript{*}}\\
		\midrule
		\showrowcolors
		\addlinespace[0.3em]
		\multicolumn{6}{l}{\textbf{Men (n = 2537)}}\\
		\addlinespace[0.3em]
		\multicolumn{6}{l}{\hspace{1em}\textbf{BMI}}\\
		\hspace{1em}\hspace{1em}Crude model & -- & -0.78 (-1.62, 0.06) & 0.068 & -0.28 (-0.96, 0.41) & 0.426\\
		\hspace{1em}\hspace{1em}Model 1\textsuperscript{\dag} & -- & -0.20 (-1.06, 0.66) & 0.654 & -0,43 (-1.13, 0.26) & 0.22\\
		\addlinespace[0.3em]
		\multicolumn{6}{l}{\hspace{1em}\textbf{BMI in non-diabetics}}\\
		\hspace{1em}\hspace{1em}Crude model & -- & -0.65 (-1.49, 0.19) & 0.127 & -0.21 (-0.89, 0.48) & 0.557\\
		\hspace{1em}\hspace{1em}Model 1\textsuperscript{\dag} & -- & -0.10 (-0.97, 0.77) & 0.82 & -0.39 (-1.10, 0.31) & 0.269\\
		\addlinespace[0.3em]
		\multicolumn{6}{l}{\textbf{Women (n = 3618)}}\\
		\addlinespace[0.3em]
		\multicolumn{6}{l}{\hspace{1em}\textbf{BMI}}\\
		\hspace{1em}\hspace{1em}Crude model & -- & -0.30 (-1.18, 0.57) & 0.496 & -0.76 (-1.44, -0.82) & 0.028\\
		\hspace{1em}\hspace{1em}Live with partner\textsuperscript{\ddag} & -- & -0.93 (-2.33, 0.46) & 0.188 & -1.76 (-2.78, -0.73) & 0.001\\
		\hspace{1em}\hspace{1em}Live alone\textsuperscript{\ddag} & -- & 1.17 (-0.35, 2.70) & 0.132 & 0.57 (-0.58, 1.719 & 0.332\\
		\addlinespace[0.3em]
		\multicolumn{6}{l}{\hspace{1em}\textbf{BMI in non-diabetics}}\\
		\hspace{1em}\hspace{1em}Crude model & -- & -0.24 (-1.12, 0.65) & 0.601 & -0.71 (-1.39, -0.03) & 0.040\\
		\hspace{1em}\hspace{1em}Live with partner\textsuperscript{\ddag} & -- & -0.86 (-2.28, 0.55) & 0.232 & -1.62 (-2.65, -0.58) & 0.002\\
		\hspace{1em}\hspace{1em}Live alone\textsuperscript{\ddag} & -- & 1.22 (-0.34, 2.78) & 0.124 & 0.43 (-0.71, 1.56) & 0.462\\
		\bottomrule
		\multicolumn{6}{l}{{\scriptsize \textit{Note: }}}\\
		\multicolumn{6}{l}{{\scriptsize \textbf{Abbreviations}: BMI body mass index; WC, waist circumference; NDNS RP, national dietary and nutrition}}\\
		\multicolumn{6}{l}{{\scriptsize  survey rolling programme.}}\\
		\multicolumn{6}{l}{{\scriptsize Diabetes was defined by A1C > 6.5\%. BMI was replaced with WC in Model 2s, other covariates remained the}}\\
		\multicolumn{6}{l}{{\scriptsize  same with the corresponding Model 1s.}}\\
		\multicolumn{6}{l}{{\scriptsize \textsuperscript{*} P values were obtained from wald tests from linear regression models.}}\\
		\multicolumn{6}{l}{{\scriptsize \textsuperscript{\dag} Adjusted for age, live with partner or not, education level, hypertension (yes or no), smoking status, total }}\\
		\multicolumn{6}{l}{{\scriptsize  energy intake, alcohol consumption;}}\\
		\multicolumn{6}{l}{{\scriptsize \textsuperscript{\ddag} Adjusted for age, average household income, education level, smoking status, total energy intake, alcohol}}\\ 
		\multicolumn{6}{l}{{\scriptsize  consumption.}}\\
	\end{tabular}
\end{table}

### 2018-08-09 paper/Tables/2by2Table1.Rmd
BMI table hypertension results added

>>>>

## Table 2 regressions for BMI

```{r tab2BMI, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
dt <- read.csv("/home/wangcc-me/Documents/LSHTMproject/Tablecsv/BMItab2.csv", header = T, row.names = NULL, colClasses = "character")
names(dt) <- c("Model", "Low", "Moderate", "P value[note]", "High", "P value")

dt[2, 1] <- c("Model 1[note]")
# dt[3, 1] <- c("Model 2[note]")
dt[6, 1] <- c("Live with partner[note]")
# dt[9, 1] <- c("Model 2[note]")

kable(dt,  align = "l", row.names = FALSE,
              format = "latex", caption = "Associations of carbohydrate eating patterns with BMI in the UK adults , with or without diabetes. (NDNS RP 2008/09-2015/16, sample size = 6155)", booktabs = T,linesep = "") %>%
 kable_styling(latex_options = c("striped"), font_size = 9) %>% 
  group_rows("Men (n = 2537)", 1, 5) %>%
  group_rows("BMI", 1, 2) %>% 
  group_rows("BMI in non-diabetics", 3, 4) %>% 
  group_rows("Women (n = 3618)", 5, 10) %>% 
  group_rows("BMI", 5, 8) %>% 
  group_rows("BMI in non-diabetics", 8, 10) %>% 
  add_header_above(c(" ", "Carbohydrate eating patterns" = 5)) %>% 
  footnote(general = c("Abbreviations: BMI body mass index; WC, waist circumference; NDNS RP, national", 
                       "dietary and nutrition survey rolling programme.",
                       "Diabetes was defined by A1C > 6.5%. BMI was replaced with WC in Model 2s, other", 
                       "covariates remained the same with the corresponding Model 1s.")) %>% 
  add_footnote(c("P values were obtained from wald tests from linear regression models.",
                "Adjusted for age, live with partner or not, education level, hypertension (yes or no), smoking status, total energy intake, alcohol consumption;", 
                "Adjusted for age, average household income, education level, smoking status, total energy intake, alcohol consumption;"),
                notation = "symbol")
```

### 2018-08-09 paper/Tables/2by2Table1.tex
BMI table hypertension results added

>>>>

\subsection{Table 2 regressions for
BMI}\label{table-2-regressions-for-bmi}

\caption{\label{tab:tab2BMI}Associations of carbohydrate eating patterns with BMI in the UK adults , with or without diabetes. (NDNS RP 2008/09-2015/16, sample size = 6155)}
\centering
\fontsize{9}{11}\selectfont
\begin{tabular}[t]{llllll}
\hiderowcolors
\toprule
\multicolumn{1}{c}{ } & \multicolumn{5}{c}{Carbohydrate eating patterns} \\
\cmidrule(l{2pt}r{2pt}){2-6}
Model & Low & Moderate & P value\textsuperscript{*} & High & P value\\
\midrule
\showrowcolors
\addlinespace[0.3em]
\multicolumn{6}{l}{\textbf{Men (n = 2537)}}\\
\addlinespace[0.3em]
\multicolumn{6}{l}{\textbf{BMI}}\\
\hspace{1em}\hspace{1em}Crude model & -- & -0.78 (-1.62, 0.06) & 0.068 & -0.28 (-0.96, 0.41) & 0.426\\
\hspace{1em}\hspace{1em}Model 1\textsuperscript{\dag} & -- & -0.20 (-1.06, 0.66) & 0.654 & -0,43 (-1.13, 0.26) & 0.22\\
\addlinespace[0.3em]
\multicolumn{6}{l}{\textbf{BMI in non-diabetics}}\\
\hspace{1em}\hspace{1em}Crude model & -- & -0.65 (-1.49, 0.19) & 0.127 & -0.21 (-0.89, 0.48) & 0.557\\
\hspace{1em}\hspace{1em}Model 1 & -- & -0.10 (-0.97, 0.77) & 0.82 & -0.39 (-1.10, 0.31) & 0.269\\
\addlinespace[0.3em]
\multicolumn{6}{l}{\textbf{Women (n = 3618)}}\\
\addlinespace[0.3em]
\multicolumn{6}{l}{\textbf{BMI}}\\
\hspace{1em}\hspace{1em}\hspace{1em}Crude model & -- & -0.30 (-1.18, 0.57) & 0.496 & -0.76 (-1.44, -0.82) & 0.028\\
\hspace{1em}\hspace{1em}Live with partner\textsuperscript{\ddag} & -- & -0.93 (-2.33, 0.46) & 0.188 & -1.76 (-2.78, -0.73) & 0.001\\
\hspace{1em}\hspace{1em}Live alone & -- & 1.17 (-0.35, 2.70) & 0.132 & 0.57 (-0.58, 1.719 & 0.332\\
\addlinespace[0.3em]
\multicolumn{6}{l}{\textbf{BMI in non-diabetics}}\\
\hspace{1em}\hspace{1em}\hspace{1em}Crude model & -- & -0.24 (-1.12, 0.65) & 0.601 & -0.71 (-1.39, -0.03) & 0.04\\
\hspace{1em}\hspace{1em}Live with partner & -- & -0.86 (-2.28, 0.55) & 0.232 & -1.62 (-2.65, -0.58) & 0.002\\
\hspace{1em}\hspace{1em}Live alone & -- & 1.22 (-0.34, 2.78) & 0.124 & 0.43 (-0.71, 1.56) & 0.462\\
\bottomrule
\multicolumn{6}{l}{\textit{Note: }}\\
\multicolumn{6}{l}{Abbreviations: BMI body mass index; WC, waist circumference; NDNS RP, national}\\
\multicolumn{6}{l}{dietary and nutrition survey rolling programme.}\\
\multicolumn{6}{l}{Diabetes was defined by A1C > 6.5\%. BMI was replaced with WC in Model 2s, other}\\
\multicolumn{6}{l}{covariates remained the same with the corresponding Model 1s.}\\
\multicolumn{6}{l}{\textsuperscript{*} P values were obtained from wald tests from linear regression models.}\\
\multicolumn{6}{l}{\textsuperscript{\dag} Adjusted for age, live with partner or not, education level, hypertension (yes or no), smoking status, total energy intake, alcohol}\\
\multicolumn{6}{l}{consumption;}\\
\multicolumn{6}{l}{\textsuperscript{\ddag} Adjusted for age, average household income, education level, smoking status, total energy intake, alcohol consumption;}\\
\end{tabular}
\end{table}
